Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-05 paper/disc20clustering.tex
Intro to LB

First, we construct a ground set of size $k-1$ on one of the clusters $S$.
In any configuration, there exists a node that accompanies it.
We only issue requests between such accompanying (time-varying) node, and any alone node that was initially collocated with it.
Repeating such requests, almost half of all node must visit the cluster $S_1$.
In comparison, \OPT performs one migration.

>>>>

First, we construct a ground set of size $k-1$ on one of the clusters $S$.
In any configuration, there exists an alone node that accompanies it.
We only issue requests between the current alone node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all node must visit the cluster $S_1$.
In comparison, \OPT performs one migration.
